Verifying Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
roberts cross and section 2 shortening

\fvset{
  linenos=true,
  fontsize=\footnotesize,
  breaklines=true,
 breakafter=w),
  xleftmargin=\parindent
}

@@

\begin{definition}[Induction variable]
  An integer variable is an \emph{induction variable} if it is the control
  variable of a \texttt{for} loop incremented by $1$ per iteration. A variable
  is interpreted as an induction variable only within the scope of the loop
  body. Induction varaibles range over $i, j, k$ throughout.
%TODO: consider mentioning derived, non-based induction variables
% as we did before.
\end{definition}

@@

Region specifications can be assigned to region variables via
region declarations. For example, the last specification
 example above can be restated as:
%%
\begin{minted}{fortran}
!= region :: r1 = centered(depth=1, dim=1) * pointed(dim=2)
!= region :: r2 = centered(depth=1, dim=2) * pointed(dim=1)
!= region :: fivePoint = r1 + r2
!= stencil fivePoint :: a
\end{minted}
This is especially useful for common stencil patterns, such as five point
stencil, as the region can be defined once and reused many times later.
%%
\paragraph{Modifiers}
%%
Region specifications can be modified
by \emph{approximation} and \emph{multiplicity} information
(in \textit{spec} in Fig.~\ref{fig:syntax}).

>>>>

\fvset{
  linenos=true,
  fontsize=\footnotesize,
  breaklines=true,
 breakafter=w),
  xleftmargin=\parindent,
  numbersep=1em
}

@@

\begin{definition}[Induction variable]
  An integer variable is an \emph{induction variable} if it is the control
  variable of a ``\texttt{for}'' loop incremented by $1$ per iteration. A variable
  is interpreted as an induction variable only within the scope of the loop
  body. Induction varaibles range over $i, j, k$ throughout.
%TODO: consider mentioning derived, non-based induction variables
% as we did before.
\end{definition}

@@

Region specifications can be assigned to region variables via
region declarations. For example, the shape of a 
``\emph{Roberts cross}'' edge-detection convolution~\cite{davis1975survey}
can be stated:
%%
\begin{minted}{fortran}
!= region :: r1 = forward(depth=1, dim=1)
!= region :: r2 = forward(depth=1, dim=2)
!= region :: robertsCross = r1*r2
!= stencil robertsCross :: a
\end{minted}
This is useful for common stencil patterns, such as the five-point
pattern, as the region can be defined once and reused.
%%
\paragraph{Modifiers}
%%
Region specifications can be modified
by \emph{approximation} and \emph{multiplicity} information
(in \textit{spec} in Fig.~\ref{fig:syntax}).
